---
title: "Predicting Heart Disease"
output:
  html_notebook: default
  html_document: default
---

# Load Packages

```{r}
library(tidyverse)
library(randomForest)
```


# Load and Tidy Data

The raw data includes the row numbers, which need to be removed. 
Moreover, the random forest model does not handle missing values,
so I need to remove any before training the model. Here, I am using
tidyr's `drop_na` to this effect. 

```{r}
heart_raw <- read.csv("../data/raw_data/Heart.csv")

heart_clean <- select(heart_raw, -X)

heart_clean <- drop_na(heart_clean)

write.csv(heart_clean, "../data/clean_data/heart.clean.csv")
```

# Train Random Forest

## Split training and test cohorts

```{r}
train <- sample(1:nrow(heart_clean), nrow(heart_clean) * 0.7)

test <- -train
```

## Train random forest model

```{r}
fit <- randomForest(AHD ~ ., data = heart_clean, subset = train, 
                    importance = TRUE, keep.forest = TRUE,
                    xtest = heart_clean[test, -ncol(heart_clean)],
                    ytest = heart_clean[test, "AHD"])
```

# Interpret Results

## Fit performance

```{r}
print(fit)
```

```{r}
plot(fit)
```


## Variable importance

```{r}
varImpPlot(fit)
```


## Effect of calcium on outcome

```{r}
partialPlot(fit, heart_clean, "Ca")
```

